Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-10 CAs_operads.tex
Corrections 3.3.2

Moreover, we run the same completion algorithm for $\CAs{\gamma}$ as
the one considered in Section~\ref{subsubsec:CAs_3}, now for
$\gamma \in [9]$. Table~\ref{tab:cardinalities_completion_CAs} shows
the number of rewrite rules needed to obtain complete orientations.
\begin{table}[ht]
    \centering
    \footnotesize
    \setlength{\tabcolsep}{.35em}
    \begin{tabular}{c||ccccccccccccccccccccccccccc}
        $\gamma$ & \multicolumn{27}{c}{
        Cardinalities of completions of $\CAs{\gamma}$}
        \\ \hline \hline
        1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        2 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        3 & 0 & 0 & 0 & 1 & 1 & 2 & 3 & 4 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        4 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 3 & 4 & 5 & 18 & 22 & 11 & 12
        & 15 & 19 & 25 & 36 & 44 & 52 & 68 & 79 & 93 & 105 & 106 & 109
        \\
        5 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 4 & 5 & 8 & 18 & 31
        & 36 & 48 & 73 & 111 & 172 & 272 & 455 & 783
        \\
        6 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 5 & 6 & 11
        & 23 & 30 & 48 & 73 & 117 & 204 & 348 & 589 & 1004
        \\
        7 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 6 & 7
        & 16 & 24 & 32 & 49 & 88 & 150 & 261 & 475 & 854
        \\
        8 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0
        & 7 & 8 & 21 & 29 & 34 & 53 & 93 & 172 & 311 & 565
        \\
        9 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0
        & 0 & 0 & 8 & 9 & 28 & 30 & 36 & 57 & 101 & 185 & 348 & 648
    \end{tabular}
    \medbreak

@@

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ when
$\gamma \geq 4$.
\medbreak

\Todo{S: j'ai supprimé les remarques concernant les générateurs multiples
car on n'en a pas du tout parlé pour l'instant. Ça a plus sa place
dans les persp.}

>>>>

Moreover, we run the same completion algorithm for $\CAs{\gamma}$ as
the one considered in Section~\ref{subsubsec:CAs_3}, now for
$\gamma \in [9]$. Table~\ref{tab:cardinalities_completion_CAs} shows
the number of rewrite rules needed to obtain complete orientations.
\begin{table}[ht]
    \centering
    \footnotesize
    \setlength{\tabcolsep}{.35em}
    \begin{tabular}{c||ccccccccccccccccccccccccccc}
        $\gamma$ & \multicolumn{27}{c}{
        Cardinalities of completions of $\CAs{\gamma}$}
        \\ \hline \hline
        1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        2 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        3 & 0 & 0 & 0 & 1 & 1 & 2 & 3 & 4 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
        \\
        4 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 3 & 4 & 5 & 18 & 22 & 11 & 12
        & 15 & 19 & 25 & 36 & 44 & 52 & 68 & 79 & 93 & 105 & 106 & 109
        & 107
        \\
        5 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 4 & 5 & 8 & 18 & 31
        & 36 & 48 & 73 & 111 & 172 & 272 & 455 & 783
        \\
        6 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 5 & 6 & 11
        & 23 & 30 & 48 & 73 & 117 & 204 & 348 & 589 & 1004
        \\
        7 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 6 & 7
        & 16 & 24 & 32 & 49 & 88 & 150 & 261 & 475 & 854
        \\
        8 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 & 0
        & 7 & 8 & 21 & 29 & 34 & 53 & 93 & 172 & 311 & 565
        \\
        9 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0
        & 0 & 0 & 8 & 9 & 28 & 30 & 36 & 57 & 101 & 185 & 348 & 648
    \end{tabular}
    \medbreak

@@

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$(\Tfr_1, \Tfr_2)$ which is not joinable, we recursively try to find a
completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ with one generator when
$\gamma \geq 4$. We discuss the cases with more than one generator in
the perspectives.
\medbreak
